### 2017-01-19 paper/modes.tex
pass in RQ2 (not done)
pass on section 2

\Mar{add a sentence to introduce this section at a higher abstraction
  level.}  Parallelism in test execution can be obtained at different
levels.  Figure~\ref{fig:levels} illustrates some of these levels.

This paper focuses at lower-level parallelism, obtained with parallel
computation at CPUs and threads in a given machine.  This kind of
parallelism is enabled through build systems and testing frameworks.
Given the proliferation of multicore machines it is not surprising
that testing frameworks provide today support for parallel test
execution with the goal of running tests more
efficiently~\cite{junit-org,testng,nunit}.  Build systems wrap
parallel features offered by testing frameworks to facilitate the use
of such technology\cite{maven-surefire-plugin}.  In the following we
elaborate relevant features of these components focusing on Java,
Maven, and JUnit but the discussion can be generalized to other
languages, build systems, and testing frameworks.

Note that lower-level parallelism is a complement to higher-level
parallelism that could be enabled through server farms.  For the
scenario of large IT organizations, lower-level parallelization
schemes could leverage the computing power of server nodes in addition
to the aggregate processing power of the farm.  Lower-level
parallelism fits particularly well smaller organizations (/projects)
with relatively high testing costs but lower budgets.
\Comment{
    Unfortunately, these solutions can't be used out-of-the-box:
    unrestricted parallel execution of tests can produce
    non-deterministic results as developers typically do not provision
    protection to concurrent accesses originated from arbitrary program
    points (\ie{}, tests).  We refer to this problem as Parallel
    Execution Flakiness (\pef{}).

@@

\subsection{Testing Framework}

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.4\textwidth]{figs/parallel-levels.pdf}
  \caption{\label{fig:levels}Levels of parallelism.}
\end{figure}

>>>>

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.35\textwidth]{figs/parallel-levels.pdf}
  \vspace{-1ex}
  \caption{\label{fig:levels}Levels of parallelism.}
\end{figure}

%\Mar{add a sentence to introduce this section at a higher abstraction
%  level.}

This section provides some background on parallel test execution.

Parallelism in test execution can be obtained at different levels.
Figure~\ref{fig:levels} illustrates relevant levels for this paper.
The highest level indicates parallelism that can be obtained through
different machines on the network.  For examples, using machines from
a cloud service.  The machine space sits under the ``network space'',
and is responsible to provide low-level parallelism.  In that case,
computation can be offloaded on different CPUs within a machine and on
different threads within each CPU.  Note that all these levels are
complementary.  For the scenario of large IT organizations, for
example, lower-level parallelization schemes could leverage the
computing power of server nodes in addition to the aggregate
processing power of the farm.

%% Lower-level parallelism fits
%% particularly well smaller organizations (/projects) with relatively
%% high testing costs but lower budgets.

This paper focuses at lower-level parallelism, which can be enabled
through build systems and testing frameworks.  Given the proliferation
of multi-core machines it is not surprising that testing frameworks
provide today support for parallel test
execution~\cite{junit-org,testng,nunit}.  Build systems wrap parallel
features offered by testing frameworks to facilitate the use of such
technology~\cite{maven-surefire-plugin}.  In the following we elaborate
relevant features of these components focusing on Java, Maven, and
JUnit but the discussion can be generalized to other languages, build
systems, and testing frameworks.

\Comment{
    Unfortunately, these solutions can't be used out-of-the-box:
    unrestricted parallel execution of tests can produce
    non-deterministic results as developers typically do not provision
    protection to concurrent accesses originated from arbitrary program
    points (\ie{}, tests).  We refer to this problem as Parallel
    Execution Flakiness (\pef{}).

@@

\Mar{----------------------- estou aqui.}

\subsection{Testing Framework}
\label{sec:frameworks}

@@
